
\section{Reflection on Project}
As my first big machine learning project, I definitely underestimated the amount of work that was needed for the project. A note for the next time - got an interesting paper that looks relatively simple? It might take more than just a couple of  hours to make it work. I guess that has a lot to do with my lack of experience of implementing large models with many parameters and configurations.

The computing power that was needed here is substantial, though my machine did a great job for the most part, and deploying the models to external machines is another skill I got thank to that project.


\section{Personal Reflection}
This project was a wild ride for me. From moments of total desperation to moments of sending images to my family to see how cool what I am doing - I had it all. 
I found this topic so interesting, that I just couldn't face the idea that I will submit a project without any new insights. Even if its not going to change the xAI world, at least its something worth reading, and not just a completely recycled versions of others papers.
I was stuck for weeks over the implementation of ScrabbleGAN that will give me the flexibility to explore the topics I wanted (the list was much much longer...).

For me, the key lesson from this project was time management and estimation - I had to bound myself to sensible goals within the given scope (and general situation, in personal life and other outer components), and I feel that I didn't managed this that way at all.